---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pelinson.et.al.2020

<!-- badges: start -->
<!-- badges: end -->

The goal of pelinson.et.al.2020 is to walk the user through the statistical analysis presented in "Pelinson et al 2020. Top predator introduction changes the effects of spatial isolation on freshwater community structure"

## Installation

You can install the last version of `pelinson.et.al.2020` package from my  [GitHub](https://github.com/RodolfoPelinson/pelinson.et.al.2020) with:


``` {r installing package, eval = T, results = "hide"}
#install.packages("devtools")
#devtools::install_github("RodolfoPelinson/pelinson.et.al.2020")
library(pelinson.et.al.2020)

```

Other packages used here are:
`vegan` version 2.5-6  
`lme4` version 1.1-23  
`emmeans` version 1.4.8  
`mvabund` version 4.1.3  
`gllvm` version 1.2.2  
`permute` version 0.9-5  

``` {r installing packages2, eval = T, results = "hide", warning = F, message = F}
library(vegan)
library(permute)
library(mvabund)
library(gllvm)
library(lme4)
```

The analysis were divided in three different sections:


[Abundance Analysis](https://github.com/RodolfoPelinson/pelinson.et.al.2020/blob/master/Abundance%20Analysis/abundance-analysis.md)  

Community Structure  

Spatial Autocorrelation Analysis  

It seems like everything is ok.
